\documentclass[../main.tex]{subfiles}

\begin{document}

This thesis was only possible due to the contributions and assistance of a number of people. First thanks goes to Evangelos Kanoulas, the academic supervisor for this work. He always kept me on track, and was full of suggestions and insights into the data and experiments I was running. Without him, I have no doubt that at the time I am writing this, this thesis would still be in the planning stages.

Special thanks also go to Wouter Koot \& Carina Dusseldorp at Buzzcapture. Wouter acted as my industry supervisor, and like Evangelos, was always on hand for support and suggestions. I very much look forward to continuing to work with and for him at Buzzcapture, following my graduation. Carina, as Head of Research at Buzzcapture, provided the data annotations that were invaluable for the smooth running of the experiments carried out on real-world data. Without her insight into the data sets that I collated, the experiments on real-world data would not have been possible to conduct in an accurate or unbiased manner.

I would also like to credit my friends Arend and Jetse, who have been excellent colleagues and friends throughout the duration of this course. Special thanks also goes to the erstwhile members of the `Beerability' WhatsApp group, set up as the informal place for our course to whinge and moan about our work. It was the one place that I could go and not feel bad about my progress.

Finally, the most important thanks go to my girlfriend, Elisabeth. She is the one that put up with the sleepless nights, the whining about workload and the days I shut myself away to finish this work. Without her, I'm not sure I would have ever had the confidence to apply to do a Masters degree in the first place.

\end{document}